PyQBench: a Python library for benchmarking gate-based quantum computers

### 2022-12-21 txt/manuscript.tex
writing.....
Fix PACS numbers
Remove instructions from "Current code version"
delete caes

\subsection{IBMQ and Lucy}

\subsection{IBMQ}
 basis gates = ["cx", "i", "rz", "sx", "x"]
\begin{figure}[h!]
\centering
\includegraphics[scale=1.2]{pics/circuit-qiskit/state_preparation-ibmq}
\caption{Circuit representing state preparation for IBMQ.}
\end{figure}
\begin{figure}[h!]
\centering
\includegraphics[scale=1.2]{pics/circuit-qiskit/u_dag-ibmq}
\caption{Circuit representing $U^\dagger$ for IBMQ.}
\end{figure}
\begin{figure}[h!]
\centering
\includegraphics[scale=1.2]{pics/circuit-qiskit/v0_dag-ibmq}
\caption{Circuit representing $V_0^\dagger$ for IBMQ.}
\end{figure}
\begin{figure}[h!]
\centering
\includegraphics[scale=1.2]{pics/circuit-qiskit/controlled_v0_v1_dag-ibmq}
\caption{Circuit representing controlled $V_0$ and $V_1$ for IBMQ.}
\end{figure}

\subsection{Lucy}
 basis gates  =["ecr", "i", "rz", "sx", "x"] 
\begin{figure}[h!]
\centering
\includegraphics[scale=1.2]{pics/circuit-qiskit/state_preparation-lucy}
\caption{Circuit representing state preparation for Lucy.}
\end{figure}
\begin{figure}[h!]
\centering
\includegraphics[scale=1.2]{pics/circuit-qiskit/u_dag-lucy}
\caption{Circuit representing $U^\dagger$ for Lucy.}
\end{figure}
\begin{figure}[h!]
\centering
\includegraphics[scale=1.2]{pics/circuit-qiskit/v0_dag-lucy}
\caption{Circuit representing $V_0^\dagger$ for Lucy.}
\end{figure}
\begin{figure}[h!]
\centering
\includegraphics[scale=1.2]{pics/circuit-qiskit/controlled_v0_v1_dag-lucy}
\caption{Circuit representing controlled $V_0$ and $V_1$ for Lucy.}
\end{figure}

\subsection{Rigetti}
 basis gates = ["cz", "rx", "rz"]
\begin{figure}[h!]
\centering
\includegraphics[scale=1.2]{pics/circuit-qiskit/state_preparation-rigetti}
\caption{Circuit representing state preparation for Rigetti.}
\end{figure}
\begin{figure}[h!]
\centering
\includegraphics[scale=1.2]{pics/circuit-qiskit/u_dag-rigetti}
\caption{Circuit representing $U^\dagger$ for Rigetti.}
\end{figure}
\begin{figure}[h!]
\centering
\includegraphics[scale=1.2]{pics/circuit-qiskit/v0_dag-rigetti}
\caption{Circuit representing $V_0^\dagger$ for Rigetti.}
\end{figure}
\begin{figure}[h!]
\centering
\includegraphics[scale=0.8]{pics/circuit-qiskit/controlled_v0_v1_dag-rigetti}
\caption{Circuit representing controlled $V_0$ and $V_1$ for Rigetti.}
\end{figure}

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%Let us consider one-qubit von Neumann measurements $\PP_U$ and $\PP_\Id$. In 
%this simplest case,  we consider two von Neumann measurements $\PP_\1$ and 
%$\PP_U$ for $U = H diag(0,\ee^{\ii \phi}) H$, where $H_d$--Hadamard matrix 
%of dimension $d$, $0 \le \phi < 2\pi$.    By theoretical results, the expected 
%probability $p_{success}$ of correct distinction between two measurements 
%$\PP_\1$ and $\PP_U$  is given by
%\begin{equation}
%p_{success} = \frac{1}{2} + \frac{1}{4} ||\PP_U - \PP_\1 ||_\diamond = 
%\frac{1}{2} + \frac{|1-\ee^{\ii \phi}|}{4}
%\end{equation}
%by the assumption the discriminator is on the form $\ket{\psi} = 
%\frac{1}{\sqrt{2}} ( \ket{00} +  \ket{11} )$. 
%(tu wyniki z rigettiego...)

@@

\begin{proof}[Proof of Proposition~\ref{prop:optimal-measurement}]
	From Proposition~\ref{prop-discrim} we obtain the exact form of discriminator given by
	\begin{equation}
	\ket{\psi_0} = | \sqrt{\rho_0}^\top \rangle \rangle = \frac{1}{\sqrt{2}} |\Id_2 
	\rangle \rangle. 
	\end{equation}
	From Holevo-Helstrom theorem  we constrain a conditional measurement $\mu$.  
	Let us define 
	\begin{equation}
	X  = \left( \PP_U \otimes \Id_2 \right)(\proj{\psi_0}) -  \left( \PP_\Id 
	\otimes \Id_2 \right)(\proj{\psi_0}).
	\end{equation} 
	From the Hahn-Jordan decomposition, let us note
	\begin{equation}
	X = P - Q
	\end{equation}
	where $P, Q \ge 0 $. 
	Let us define projectors $\Pi_P$ and $\Pi_Q$ onto  $\text{im}(P)$ and $\text{im}(Q)$, 
	respectively. Observe, that $P $ and $Q$ are block-diagonal.  Then,  $\Pi_P$ and $\Pi_Q$ have the following forms
	\begin{equation}
	\Pi_P = \left(\begin{array}{cc}\proj{x_p}&0\\0&\proj{y_p}\end{array}\right) 
	\end{equation}
	and 
	\begin{equation}
	\Pi_Q = \left(\begin{array}{cc}\proj{x_q}&0\\0&\proj{y_q}\end{array}\right). 
	\end{equation}
	Hence, we define $V_0$ as
	\begin{equation}
	\begin{cases} V_0 \ket{x_p} = \ket{0} \\ V_0 \ket{x_q} = \ket{1} \end{cases}
	\end{equation}
	and $V_1$ as
	\begin{equation}
	\begin{cases} 
	V_1 \ket{y_p} = \ket{0} \\ 
	V_1 \ket{y_q} = \ket{1}
	\end{cases}. 
	\end{equation}
	For the discrimination task between $\PP_{U}$ and $\PP_{\Id}$, where $U = H 
	\diag(1, e^{i \phi })H$, the explicit form of $V_0$ and $V_1$ is given as 
	follows \todo[inline]{udostepniamy ten plik nb?}(see also \texttt{one-qubit.nb}).
	The unitary $V_0$ has the form
	\begin{equation}
	V_0 = \left(
	\begin{array}{cc}i \sin\left( \frac{\pi - \phi}{4} \right)&-i 
	\cos\left( \frac{\pi - \phi}{4} \right)\\ \cos\left( \frac{\pi - 
		\phi}{4}\right)& \sin\left( \frac{\pi - \phi}{4} \right)
	\end{array}
	\right),
	\end{equation}
	whereas the unitary  $V_1$  has the form
	\begin{equation}
	V_1 = \left(\begin{array}{cc}-i \cos\left(\frac{\pi - \phi}{4}\right) &i 
	\sin\left( \frac{\pi - \phi}{4}\right)\\\sin\left( \frac{\pi - \phi}{4} 
	\right) &  \cos\left( \frac{\pi - \phi}{4} \right) \end{array}\right),
	\end{equation}
	for all $\phi \in [0,2\pi)$. 
	Finally, we obtain the measurement $\mu$ of the form
	\begin{equation}
	\begin{split}
	\mu(0) = \proj{0} \otimes V_0 \proj{0} V_0^\dagger +  \proj{1} \otimes V_1 
	\proj{0} V_1^\dagger, \\ 
	\mu(1) = \proj{0} \otimes V_0 \proj{1} V_0^\dagger +  \proj{1} \otimes V_1 
	\proj{1} V_1^\dagger.  
	\end{split}
	\end{equation} 
\end{proof}

>>>>

\subsection{Lucy}
 basis gates  =["ecr", "i", "rz", "sx", "x"]

\subsection{Rigetti}
 basis gates = ["cz", "rx", "rz"]

@@

@@

\begin{proof}[Proof of Proposition~\ref{prop:optimal-measurement}]
	From Proposition~\ref{prop-discrim} we obtain the exact form of discriminator given by
	\begin{equation}
	\ket{\psi_0}  = \frac{1}{\sqrt{2}} |\Id_2 
	\rangle \rangle. 
	\end{equation}
	From Holevo-Helstrom theorem  we constrain a conditional measurement $\mu$.  
	Let us define 
	\begin{equation}
	X  = \left( \PP_U \otimes \Id_2 \right)(\proj{\psi_0}) -  \left( \PP_\Id 
	\otimes \Id_2 \right)(\proj{\psi_0}).
	\end{equation} 
	From the Hahn-Jordan decomposition, let us note
	\begin{equation}
	X = P - Q
	\end{equation}
	where $P, Q \ge 0 $. 
	Let us define projectors $\Pi_P$ and $\Pi_Q$ onto  $\text{im}(P)$ and $\text{im}(Q)$, 
	respectively. Observe, that $P $ and $Q$ are block-diagonal.  Then,  $\Pi_P$ and $\Pi_Q$ have the following forms
	\begin{equation}
	\Pi_P = \left(\begin{array}{cc}\proj{x_p}&0\\0&\proj{y_p}\end{array}\right) 
	\end{equation}
	and 
	\begin{equation}
	\Pi_Q = \left(\begin{array}{cc}\proj{x_q}&0\\0&\proj{y_q}\end{array}\right). 
	\end{equation}
	Hence, we define $V_0$ as
	\begin{equation}
	\begin{cases} V_0 \ket{x_p} = \ket{0} \\ V_0 \ket{x_q} = \ket{1} \end{cases}
	\end{equation}
	and $V_1$ as
	\begin{equation}
	\begin{cases} 
	V_1 \ket{y_p} = \ket{0} \\ 
	V_1 \ket{y_q} = \ket{1}
	\end{cases}. 
	\end{equation}
	For the discrimination task between $\PP_{U}$ and $\PP_{\Id}$, where $U = H 
	\diag(1, e^{i \phi })H$, the explicit form of $V_0$ and $V_1$ is given as 
	follows \todo[inline]{udostepniamy ten plik nb?}(see also \texttt{one-qubit.nb}).
	The unitary $V_0$ has the form
	\begin{equation}
	V_0 = \left(
	\begin{array}{cc}i \sin\left( \frac{\pi - \phi}{4} \right)&-i 
	\cos\left( \frac{\pi - \phi}{4} \right)\\ \cos\left( \frac{\pi - 
		\phi}{4}\right)& \sin\left( \frac{\pi - \phi}{4} \right)
	\end{array}
	\right),
	\end{equation}
	whereas the unitary  $V_1$  has the form
	\begin{equation}
	V_1 = \left(\begin{array}{cc}-i \cos\left(\frac{\pi - \phi}{4}\right) &i 
	\sin\left( \frac{\pi - \phi}{4}\right)\\\sin\left( \frac{\pi - \phi}{4} 
	\right) &  \cos\left( \frac{\pi - \phi}{4} \right) \end{array}\right),
	\end{equation}
	for all $\phi \in [0,2\pi)$. 
	Finally, we obtain the measurement $\mu$ of the form
	\begin{equation}
	\begin{split}
	\mu(0) = \proj{0} \otimes V_0 \proj{0} V_0^\dagger +  \proj{1} \otimes V_1 
	\proj{0} V_1^\dagger, \\ 
	\mu(1) = \proj{0} \otimes V_0 \proj{1} V_0^\dagger +  \proj{1} \otimes V_1 
	\proj{1} V_1^\dagger.  
	\end{split}
	\end{equation} 
\end{proof}
